\documentclass[11pt,letterpaper,titlepage]{article}

\usepackage{geometry}
\geometry{left=2cm,right=2cm,top=2cm,bottom=3cm}

\usepackage{setspace}
\onehalfspacing

\usepackage{multicol}
\setlength{\columnsep}{3em}

\usepackage{booktabs}

\usepackage[table,x11names]{xcolor}

\usepackage{multirow}

\usepackage{pgfgantt}

\usepackage{listings}

\usepackage{xcolor}
\definecolor{vgreen}{RGB}{104,180,104}
\definecolor{vblue}{RGB}{49,49,255}
\definecolor{vorange}{RGB}{255,143,102}

\lstdefinestyle{C-style}
{
    language=C,
    basicstyle=\small\ttfamily,
    keywordstyle=\color{vblue},
    identifierstyle=\color{black},
    commentstyle=\color{vgreen},
    % numbers=left,
    numberstyle=\tiny\color{black},
    numbersep=11pt,
    tabsize=4,
    moredelim=*[s][\colorIndex]{[}{]},
    literate=*{:}{:}1
}

\lstdefinestyle{txt-style}
{
    basicstyle=\small\ttfamily,
    % numbers=left,
    numbersep=11pt,
    tabsize=4,
    moredelim=*[s][\colorIndex]{[}{]},
    literate=*{:}{:}1
}

\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows, positioning, fit,calc}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,draw,inner sep=1pt] (char) {#1};}}
            
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=black
}

\usepackage{pifont}

\usepackage[toc,page]{appendix}

\pagestyle{empty}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}

\usetikzlibrary{mindmap,trees}
\usepackage{verbatim}

\usepackage{indentfirst}
\setlength{\parindent}{2em}

\usepackage{listings}

% \usepackage{hyperref}
\usepackage{chngcntr}
\counterwithin{section}{part}
\renewcommand\thesection{\arabic{section}}

\usepackage{graphicx}

\usepackage{subcaption}

\usepackage{fancyhdr}

\pagestyle{fancy}
\lhead{}
\rhead{}
\lfoot{ECEN 749 Section 601 Lab 3}
\cfoot{\thepage}
\rfoot{@Lei Wang (Wilson)}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\headwidth}{\textwidth}
\renewcommand{\footrulewidth}{0.4pt}
\newcommand{\RomanNumeralCaps}[1]
    {\MakeUppercase{\romannumeral #1}}

\makeatletter
\newcommand*\@lbracket{[}
\newcommand*\@rbracket{]}
\newcommand*\@colon{:}
\newcommand*\colorIndex{%
    \edef\@temp{\the\lst@token}%
    \ifx\@temp\@lbracket \color{black}%
    \else\ifx\@temp\@rbracket \color{black}%
    \else\ifx\@temp\@colon \color{black}%
    \else \color{vorange}%
    \fi\fi\fi
}
\makeatother

\usepackage{trace}

\begin{document}

\begin{titlepage}
  \centering
	{\scshape\large Texas A\&M University \par}
	\vspace{1cm}
	{\scshape\Large Department of Electrical and Computer Engineering \par}
	\vspace{4cm}
    \vspace{0.5cm}
	{\huge\bfseries ECEN 749 Microprocessor System Design\par}
	\vspace{4cm}
	{\Large Lab 2 Report (Section 601)\par}
	\vspace{1cm}
	{\Large Student: Lei Wang (Wilson)\par}
	\vspace{1cm}
	{\Large UIN: 829009485\par}
	\vspace{1cm}
	{\Large Instructor: Dr. Paul V. Gratz\par}
	\vspace{4cm}
	\vfill

  % Bottom of the page
	{\large Submitted: February 11th, 2020 \par}

\end{titlepage}

\newpage

\tableofcontents{}

\newpage

\part{Introduction}

The lab session aims at teaching students build their own IP, integrate the IP into the system and use C to use the IP. The lab focuses on a simple hardware multiplier implementation and no longer uses the soft processor introduced in the previous lab.

\part{Procedure}

\begin{enumerate}
    \item Create a Vivado project in a new folder. When selecting the hardware, choose \textbf{Boards} $\rightarrow$ \textbf{Zybo Z7-10}.
    
    \item Create a block design schematic with the \textbf{ZYNQ7 Processing System} IP added. Name the block design \textbf{Multiply}.
    
    \item Configure the \textbf{ZYNQ7 Processing System} IP by double clicking on it. Download the \textbf{.tcl} file provided for the lab session to the Vivado project directory. Click on \textbf{Presets} $\rightarrow$ \textbf{Apply Configuration} in the \textbf{Re-customize IP} window. Select the downloaded \textbf{.tcl} file. Uncheck all peripheral I/O pins but \textbf{UART 1} in the \textbf{Peripheral I/O Pins} tab.
    
    \item Click on \textbf{Tools} $\rightarrow$ \textbf{Create and Package IP} to open the \textbf{Create and Package New IP} window. Click on \textbf{Next} $\rightarrow$ \textbf{Create a new AXI4 peripheral} $\rightarrow$ \textbf{Next}.
    
    \item Give the IP a name and a short description. Keep the version number unchanged. Click on \textbf{Next}.
    
    \item Configure \textbf{Interface} according to the following table:
    
    \begin{table}[ht]
    \centering
    \begin{tabular}{@{}llll@{}}
    \toprule
    \begin{tabular}[c]{@{}l@{}}Interface\\ type:\end{tabular} & \begin{tabular}[c]{@{}l@{}}Interface\\ mode:\end{tabular} & \begin{tabular}[c]{@{}l@{}}Data\\ width:\end{tabular} & \begin{tabular}[c]{@{}l@{}}Number of\\ registers:\end{tabular} \\ \midrule
    Lite                                                      & Slave                                                     & 32                                                    & 4                                                              \\ \bottomrule
    \end{tabular}
    \caption{New IP interface configuration}
    \end{table}
    
    Check \textbf{Edit IP} and click \textbf{Finish}.
    
    \item Open \textbf{multiply\_v1\_0\_S00\_AXI.v} in the \textbf{source} window under \textbf{multiply\_v1\_0}. Comment out code that modifies value in \textbf{slv\_reg2}.
    
    \item Find the line \textbf{//Add user logic here}. Add the following code:
    
    \lstinputlisting[style={txt-style}]{added_Verilog.txt}
    
    \item Click on \textbf{Review and Package} $\rightarrow$ \textbf{Re-package} in the \textbf{Package IP} tab. Close the customized-IP project when done.
    
    \item Go back to the Vivado project that contains the ZYNQ processing system and Add the multiplier IP that is created. Run connection automation. Remember to select \textbf{All Automation}.
    
    \item Regenerate layout. The finished layout should look like the following:
    
    % add the screenshot here
    
    \item Create HDL wrapper for the block design in the source tab.
    
    \item Generate the bitstream.
    
    \item Export the design, including the bitstream.
    
    \item Launch the Xilinx SDK. 
    
\end{enumerate}

% add screenshots on the arrangement of the hardware in the block diagram

% add the screenshot of the picocom output

\part{Results}

\newpage

\part{Conclusion}

\textbf{Q: What is the purpose of the tmp\_reg from the Verilog code provided in lab, and what happens if
this register is removed from the code?}

A:

\textbf{Q: What values of ‘slv\_reg0’ and ‘slv\_reg1’ would produce incorrect results from the multiplication
block? What is the name commonly assigned to this type of computation error, and how would
you correct this? Provide a Verilog example and explain what you would change during the
creation of the corrected peripheral.}

A:

\newpage

\begin{appendices}

\section{Multiplier.c}
\label{appendix:multiplier_c}
\lstinputlisting[style={C-style}]{lab3.c}

\end{appendices}

\end{document}
